\mytitle

### 2023-05-25 generated/over-fitting-code-section.tex
fixing final bugs

\subsection{The siren call of over-fitting code}\label{over-fit}
%Science is a methodical process that constructs principles and theories that describe the world, and competitive peer reviewed publication is the reliable record of that. We do the science, and we are in the world, so there are challenging meta-theoretical issues as well as practical experimental and resourcing issues. Karl Popper is one of many philosophers of science to develop principles and theories about science \cite{popper-three-worlds,popper-conjectures-refutations}.

%Popper was concerned with the conventional sciences, where the world, Nature, is assumed fixed and in principle knowable. Writing just six years after Popper, Herbert Simon introduced the ``sciences of the artificial'' \cite{sciences-artificial}, which instead focus on understanding artificial worlds, most typically computer programs. Programs effectively create worlds, and the sciences of the artificial seek to understand and improve those worlds. Crucially, there is no philosophical or other reason why artificial worlds should be based on principles, let alone be simple or elegant. Conventional science's \ae sthetics need not apply.

%Science to date has been inevitably driven by human \ae sthetics: that is, simple, elegant, understandable, beautiful, brief, exciting, intelligible \ldots\ all are human properties that are applied to doing, funding, defining, and selecting ``good'' science.

\noindent
Poor code undermines scientific quality: poor code can generate plausible and possibly misleading results from \emph{any\/} data, including even fictional science. A temptation is that %artificial world \cite{sciences-artificial}, built on
adjusting the code's results gets more attention than the theoretical basis of the code's overall faithfulness to the experimental phenomena. 
% wolframscript (if being used) unnecessarily prints the next 2 lines (generated by CellPrint), but they are needed!
\def\imageWidthCalculation{\multiply \imageWidth by 21 \divide \imageWidth by 28}
\def\figureStarDetails{*}

@@

%\vfill % the vfill is only needed to put the box at the bottom of a column if that makes it look better
\vskip 1ex
\noindent 
{\newdimen\boxwidth
\boxwidth = \columnwidth
\advance\boxwidth by - 1em
\begin{tabular}{@{}l@{}}
\framebox[\columnwidth][r]{\hfill\parbox{\boxwidth}{This section (\ref{over-fit}) of this paper, including figure \ref{fig-overfit}, was generated as a computational paper in a \emph{Mathematica\/} notebook, then exported to \LaTeX\ to include here. The \supplement\ provides a more complete explanation, as well as the data and details of the fitted polynomials (also generated automatically). This paper's repository includes the notebook.

%\hskip 1em Generated text and data presented elsewhere in this paper were created by a \texttt{make} file running shell scripts and JavaScript code analyzing repositories, JSON survey data, etc. Results were exported to files of \LaTeX\ markup and definitions, then imported into this paper and expanded where needed.
}\hfill}\end{tabular}}

>>>>

\subsection{The siren call of over-fitting code}\label{over-fit}
Poor code undermines scientific quality: poor code can generate plausible and possibly misleading results from \emph{any\/} data, including even fictional science. A temptation is that %artificial world \cite{sciences-artificial}, built on adjusting the code's results gets more attention than the theoretical basis of the code's overall faithfulness to the experimental phenomena. 
% wolframscript (if being used) unnecessarily prints the next 2 lines (generated by CellPrint), but they are needed!
\def\imageWidthCalculation{\multiply \imageWidth by 21 \divide \imageWidth by 28}
\def\figureStarDetails{*}

@@

### 2023-05-25 paper-seb-main.tex
fixing final bugs

%\color{blue}
\input generated/over-fitting-code-section.tex
%\color{black}

@@

\newcount \enum
\enum=1
\renewcommand{\theenumi}{\ifnum \enum<10 \hphantom{0}\fi
\the\enum
\global\advance \enum by 1}
\begin{enumerate}\raggedright
\item Is the code valid: does it do what the paper claims?\footnote{Of course, the underlying science may be wrong to, so it is useful to distinguish \emph{internal validity\/} and \emph{external validity}. Internal validity occurs if the code does what the paper claims; external validity occurs if the code represents correct science (which the paper may have interpreted incorrectly.}
\item Do other scientists, including reviewers and the authors, understand the code?
\item Does the code implement the methods described in the paper?
\item Has the code been over-fitted or tweaked to support specific claims in the paper?'
\item Is there a definitive version of code?
\item Is the code controlled and signed?
\item What limitations does the code have?
\item Was the code developed to any standard, and does it comply to that standard?
\item How does the code protect against data, coding, and human error?
\item Was the code tested adequately?
\item Does the code depend on arbitrary parameters, data, or code to over-fit to obtain the published results?
\item Is the code documented adequately, so we know what it is trying to do, and how?
\item \ldots\ and so forth --- questions are numbered for reference. 
\end{enumerate}

@@

Because of the recognized importance of the Ferguson paper, a project started to document its code  \cite{refactoring}.\footnote{The system is now opeve it, so it is surprising to find an undocumented model being used in the first place, since so many years' opportunity to improve the code have been lost. The revised code has now been published, and it too has been heavily criticized \citeeg{bad-code}, supporting the concerns expressed in the present paper.
n-source, available at \url{github.com/mrc-ide/covid-sim} version (19 July 2021).} Documenting code in hindsight, even if done rigorously, may describe what it does, \emph{including\/} its bugs, but it is unlikely to explain what it was originally intended to have done. As the code is documented, bugs will be found, which will then be fixed (refactoring), and so the belatedly-documented code will not be the code that was used in the published models; it will be different.

@@

\subsection{Action must be interdisciplinary}
\setcounter{footnote}{1}
Code is more than a scientific instrument, more than a thermometer or test tube, as code makes, informs and changes decisions; indeed, code can actually \emph{do\/} science. Still, code is only a part of science, so relying on SEBs \emph{alone\/} would continue one of the besetting problems about the role of code in science.

@@

Journal policies could start to explicitly encourage computationally reproducible science using RAP and \RAPstar\ techniques. That is, the research's methodology itself may be a mixture of data and code. As this paper's \supplement\ shows in section \ref{restrictive-policies}, many journals (e.g., \emph{PLOS ONE\/} and, ironically, \emph{IEEE Transactions on Software Engineering\/}) and repositories have policies that make RAP much harder or just counter-productive at the last step.

@@

\makeatletter
\immediate\write\@auxout{\string\def\string\continueSectionNumbers{\arabic{section}}}
\makeatother

@@

%\nolinenumbers

@@

\bibliographystyle{revisedCompJ}
\def\urlprefix{}
\initialiseBibliography{References}{1}{}

\newcount \bibitemn \bibitemn = 0
\newcount \bibnewcolumn 
w
\bibnewcolumn = 122 % bibentry number of last entry on (final) left hand column
% Hint: set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!

@@

%\label{LastPage}
%save Latex register    {linenumber}
%\makeatletter
%\immediate\write\@auxout{\string\def\string\MainPaperLastLine{\arabic{linenumber}}}
%\makeatother
\end{document}

>>>>

\input generated/over-fitting-code-section.tex

@@

\newcount \enum
\enum=1
\renewcommand{\theenumi}{\ifnum \enum<10 \hphantom{0}\fi
\the\enum
\global\advance \enum by 1}
\begin{enumerate}\raggedright
\item Is the code valid: does it do what the paper claims?\footnote{Of course, the underlying science may be wrong to, so it is useful to distinguish \emph{internal validity\/} and \emph{external validity}. Internal validity occurs if the code does what the paper claims; external validity occurs if the code represents correct science which the paper may have interpreted incorrectly.}
\item Do other scientists, including reviewers and the authors, understand the code?
\item Does the code implement the methods described in the paper?
\item Has the code been over-fitted or tweaked to support specific claims in the paper?'
\item Is there a definitive version of code?
\item Is the code controlled and signed?
\item What limitations does the code have?
\item Was the code developed to any standard, and does it comply to that standard?
\item How does the code protect against data, coding, and human error?
\item Was the code tested adequately?
\item Does the code depend on arbitrary parameters, data, or code to over-fit to obtain the published results?
\item Is the code documented adequately, so we know what it is trying to do, and how?
\item \ldots\ and so forth --- questions are numbered for reference. 
\end{enumerate}

@@

Because of the recognized importance of the Ferguson paper, a project started to document its code  \cite{refactoring}.\footnote{It is surprising to find an undocumented model being used in the first place, since so many years' opportunity to improve the code have been lost. The revised code has now been published, and it too has been heavily criticized \citeeg{bad-code}, supporting the concerns expressed in the present paper.
n-source, available at \url{github.com/mrc-ide/covid-sim} version (19 July 2021).} Documenting code in hindsight, even if done rigorously, may describe what it does, \emph{including\/} its bugs, but it is unlikely to explain what it was originally intended to have done. As the code is documented, bugs will be found, which will then be fixed (refactoring), and so the belatedly-documented code will not be the code that was used in the published models; it will be different.

@@

\subsection{Action must be interdisciplinary}
Code is more than a scientific instrument, more than a thermometer or test tube, as code makes, informs and changes decisions; indeed, code can actually \emph{do\/} science. Still, code is only a part of science, so relying on SEBs \emph{alone\/} would continue one of the besetting problems about the role of code in science.

@@

\label{mentionPLOSandIEEE}
Journal policies could start to explicitly encourage computationally reproducible science using RAP and \RAPstar\ techniques. That is, the research's methodology itself may be a mixture of data and code. As this paper's \supplement\ shows in section \ref{restrictive-policies}, many journals (e.g., \emph{PLOS ONE\/} and, ironically, \emph{IEEE Transactions on Software Engineering\/}) and repositories have policies that make RAP much harder or just counter-productive at the last step.

@@

@@

@@

\bibliographystyle{revisedCompJ}
\def\urlprefix{}

\initialiseBibliography{References}{1}{}

\newcount \bibitemn \bibitemn = 0
\newcount \bibnewcolumn

\bibnewcolumn = 122 % bibentry number of last entry on (final) left hand column
% Hint: first set it to a very large number, so the final column is as unbalanced as it gets
% then, if it's worth fixing the final page, lower the number to some citation on the 
% lower part of the left hand column; this citation will then become the last in that
% column. Hopefully the righthand column will be of equal length!
% PS Don't forget to check there is nothing on the following page!

@@

\makeatletter
\immediate\write\@auxout{\string\def\string\continueSectionNumbers{\arabic{section}}}
\immediate\write\@auxout{\string\def\string\continueTableNumbers{\arabic{table}}}
\immediate\write\@auxout{\string\def\string\continueFigureNumbers{\arabic{figure}}}
\immediate\write\@auxout{\string\def\string\continueFootnoteNumbers{\arabic{footnote}}}
\immediate\write\@auxout{\string\def\string\continuePageNumbers{\arabic{page}}}
\makeatother
